---
title: "MIMICS: ANPP Sensitivity"
output:
  html_document:
    code_folding: hide
  pdf_document: default
always_allow_html: true
---

```{r message=FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(knitr)
library(DT)
library(gridExtra)
library(grid)
library(readxl)
library(leaflet)
library(viridis)
library(reshape)

#for MIMICS
library(rootSolve)
library(boot)

options(ggplot2.continuous.colour="viridis")
options(ggplot2.continuous.fill = "viridis")
options(width = 100)
```


```{r echo=FALSE, message=FALSE, results=FALSE, out.width = '80%' }
# -----------------------------------------------------------
# MIMICS2_RXEQ function
# -----------------------------------------------------------

#REVERSE MODEL 
RXEQ <- function(t, y, pars) {
  with (as.list(c(y, pars)),{
    
    #Flows to and from MIC_1
    LITmin[1] = MIC_1 * VMAX[1] * LIT_1 / (KM[1] + MIC_1)   #MIC_1 decomp of MET lit
    LITmin[2] = MIC_1 * VMAX[2] * LIT_2 / (KM[2] + MIC_1)   #MIC_1 decomp of STRUC lit
    MICtrn[1] = MIC_1 * tau[1]  * fPHYS[1]                  #MIC_1 turnover to PHYSICAL SOM 
    MICtrn[2] = MIC_1 * tau[1]  * fCHEM[1]                  #MIC_1 turnover to CHEMICAL SOM  
    MICtrn[3] = MIC_1 * tau[1]  * fAVAI[1]                  #MIC_1 turnover to AVAILABLE SOM  
    SOMmin[1] = MIC_1 * VMAX[3] * SOM_3 / (KM[3] + MIC_1)   #decomp of SOMa by MIC_1
    
    #Flows to and from MIC_2
    LITmin[3] = MIC_2 * VMAX[4] * LIT_1 / (KM[4] + MIC_2)   #decomp of MET litter
    LITmin[4] = MIC_2 * VMAX[5] * LIT_2 / (KM[5] + MIC_2)   #decomp of SRUCTURAL litter
    MICtrn[4] = MIC_2 * tau[2]  * fPHYS[2]                  #MIC_2 turnover to PHYSICAL  SOM 
    MICtrn[5] = MIC_2 * tau[2]  * fCHEM[2]                  #MIC_2 turnover to CHEMICAL  SOM  
    MICtrn[6] = MIC_2 * tau[2]  * fAVAI[2]                  #MIC_2 turnover to AVAILABLE SOM  
    SOMmin[2] = MIC_2 * VMAX[6] * SOM_3 / (KM[6] + MIC_2)   #decomp of SOMa by MIC_2
    
    DEsorb    = SOM_1 * desorb  #* (MIC_1 + MIC_2)  	#desorbtion of PHYS to AVAIL (function of fCLAY)
    OXIDAT    = ((MIC_1 * VMAX[2] * SOM_2 / (KO[1]*KM[2] + MIC_1)) +
                 (MIC_2 * VMAX[5] * SOM_2 / (KO[2]*KM[5] + MIC_2)) )  #oxidation of C to A

    dLIT_1 = I[1]*(1-FI[1]) - LITmin[1] - LITmin[3]
    dMIC_1 = CUE[1]*(LITmin[1]+ SOMmin[1]) + CUE[2]*(LITmin[2]) - sum(MICtrn[1:3])
    dSOM_1 = I[1]*FI[1] + MICtrn[1] + MICtrn[4]- DEsorb 
    
    dLIT_2 = I[2] * (1-FI[2]) - LITmin[2] - LITmin[4]
    dMIC_2 = CUE[3]*(LITmin[3]+ SOMmin[2]) + CUE[4]*(LITmin[4]) - sum(MICtrn[4:6])  
    dSOM_2 = I[2]*FI[2] + MICtrn[2] + MICtrn[5] - OXIDAT
    
    dSOM_3 = MICtrn[3] + MICtrn[6] + DEsorb + OXIDAT - SOMmin[1] - SOMmin[2]
    
    list(c(dLIT_1, dLIT_2, dMIC_1, dMIC_2, dSOM_1, dSOM_2, dSOM_3))
  })
}
```

## How does shifting ANPP change MIMICS SOC estimates?
Especially important as we're ballparking the ANPP number form the GPP estimate (pGPP). How much does it matter if we pGPP vs. pGPP/2 vs pGPP/3? etc. 

<br>

### MIMICS with initial parameters

Using pGPP+400/2 for ANPP, mean LiDET fMET, and no fW.


```{r message=FALSE, results=FALSE, out.width = '80%' }
## Starting parameters
  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+400)/2
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV  #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=(pGPP+400)/2)) + geom_point() +
  scale_color_gradient(low="blue", high="red") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("SOC vs MIMICS SOC estimate") + 
  xlim(0,15)
MIM_plot

#save data table for use later
colnames(table)[1] <- "Site"
MIMout <- suppressWarnings(
  as.data.frame(data) %>% full_join(as.data.frame(table))
)
```


```{r message=FALSE, results=FALSE, out.width = '80%' }

MIMout_pool_melt <- MIMout %>% gather(key = 'SOM_pool', value = 'SOM_size', SOMp:SOMa)
MIMout_smry <- MIMout_pool_melt %>% group_by(Site, SOM_pool)# %>%
                #summarise(Ccontent_mean = mean(Ccontent),
                #          Ccontent_se = sd(Ccontent)/sqrt(n()))

MIMout_smry$SOM_size <- as.numeric(MIMout_smry$SOM_size)

MIMout_smry$SOM_size_norm <- ave(MIMout_smry$SOM_size, MIMout_smry$Site, FUN=function(x) x/sum(x))

ggplot(MIMout_smry, aes(x=reorder(Site, pGPP+400), y=SOM_size_norm, fill=factor(SOM_pool, levels=c("SOMa", "SOMc", "SOMp")))) +  
         theme_bw() +
         geom_bar(position="stack", stat = "identity") +
         scale_fill_manual(values=c("#adb36e", "#ff9a8c","#ea2c62"), labels=c("SOMa", "SOMc", "SOMp")) + labs(fill="MIMSOC Pool") +
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) +
  scale_y_continuous(expand = c(0, 0)) +
  xlab("Estimated GPP Increases -->") + 
  ylab("mg C g-1 bulk soil") +
  ggtitle("RC MIMSOC pools by SOM input quantity")
```





## Drop ANPP by half

ANPP = (pGPP+400)/4

Result: Dropping ANPP values scrunches MIMSOC estimates into a lower, but tighter range of values == worse


```{r message=FALSE, results=FALSE, out.width = '80%' }
## Starting parameters
  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+400)/4
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV  #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=(pGPP+400)/4)) + geom_point() +
  scale_color_gradient(low="blue", high="red") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("SOC vs MIMICS SOC estimate") + 
  xlim(0,15)
MIM_plot

#save data table for use later
colnames(table)[1] <- "Site"
MIMout <- suppressWarnings(
  as.data.frame(data) %>% full_join(as.data.frame(table))
)
```

```{r message=FALSE, results=FALSE, out.width = '80%' }

MIMout_pool_melt <- MIMout %>% gather(key = 'SOM_pool', value = 'SOM_size', SOMp:SOMa)
MIMout_smry <- MIMout_pool_melt %>% group_by(Site, SOM_pool)# %>%
                #summarise(Ccontent_mean = mean(Ccontent),
                #          Ccontent_se = sd(Ccontent)/sqrt(n()))

MIMout_smry$SOM_size <- as.numeric(MIMout_smry$SOM_size)

MIMout_smry$SOM_size_norm <- ave(MIMout_smry$SOM_size, MIMout_smry$Site, FUN=function(x) x/sum(x))

ggplot(MIMout_smry, aes(x=reorder(Site, pGPP+400), y=SOM_size_norm, fill=factor(SOM_pool, levels=c("SOMa", "SOMc", "SOMp")))) +  
         theme_bw() +
         geom_bar(position="stack", stat = "identity") +
         scale_fill_manual(values=c("#adb36e", "#ff9a8c","#ea2c62"), labels=c("SOMa", "SOMc", "SOMp")) + labs(fill="MIMSOC Pool") +
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) +
  scale_y_continuous(expand = c(0, 0)) +
  xlab("Estimated GPP Increases -->") + 
  ylab("mg C g-1 bulk soil") +
  ggtitle("RC MIMSOC pools by SOM input quantity")
```


## Increase ANPP? Will that further improve the slope of our estimates? tighter residual error?

ANPP = pGPP+400

Result: Slope looke good, but the model is storing way to much C as SOMp. This makes sense since we ramped up microbial processing with the additional inputs. 

**Take away:** It's the lower end resistance in MIMICS that we need to change. Why will MIMICS not predict an SOC below ~3 kg C m-2 even if the ANPP value is very small?


```{r message=FALSE, results=FALSE, out.width = '80%' }
## Starting parameters
  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+400)
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV  #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=pGPP+400)) + geom_point() +
  scale_color_gradient(low="blue", high="red") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("SOC vs MIMICS SOC estimate") + 
  xlim(0,15)
MIM_plot

#save data table for use later
colnames(table)[1] <- "Site"
MIMout <- suppressWarnings(
  as.data.frame(data) %>% full_join(as.data.frame(table))
)
```

```{r message=FALSE, results=FALSE, out.width = '80%' }

MIMout_pool_melt <- MIMout %>% gather(key = 'SOM_pool', value = 'SOM_size', SOMp:SOMa)
MIMout_smry <- MIMout_pool_melt %>% group_by(Site, SOM_pool)# %>%
                #summarise(Ccontent_mean = mean(Ccontent),
                #          Ccontent_se = sd(Ccontent)/sqrt(n()))

MIMout_smry$SOM_size <- as.numeric(MIMout_smry$SOM_size)

MIMout_smry$SOM_size_norm <- ave(MIMout_smry$SOM_size, MIMout_smry$Site, FUN=function(x) x/sum(x))

ggplot(MIMout_smry, aes(x=reorder(Site, pGPP+400), y=SOM_size_norm, fill=factor(SOM_pool, levels=c("SOMa", "SOMc", "SOMp")))) +  
         theme_bw() +
         geom_bar(position="stack", stat = "identity") +
         scale_fill_manual(values=c("#adb36e", "#ff9a8c","#ea2c62"), labels=c("SOMa", "SOMc", "SOMp")) + labs(fill="MIMSOC Pool") +
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) +
  scale_y_continuous(expand = c(0, 0)) +
  xlab("Estimated GPP Increases -->") + 
  ylab("mg C g-1 bulk soil") +
  ggtitle("RC MIMSOC pools by SOM input quantity")
```



## Plot MIMSOC vs ANPP
```{r message=FALSE, results=FALSE, out.width = '80%' }
## Starting parameters
  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+200)
  #convert negative ANPP to a small number 
  ANPP <- ifelse(ANPP < 0, 0.1, ANPP)
  
  
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV  #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
    
    #extra prints
        #extra parameters to store in table
    #print(paste0("r input: ", as.character(I[1])))
    #print(paste0("MIMSOC: ", as.character(MIMSOC[i])))      
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=ANPP)) + geom_point() +
  scale_color_gradient(low="blue", high="red") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("SOC vs MIMICS SOC estimate") + 
  xlim(0,15)
MIM_plot

#save data table for use later
colnames(table)[1] <- "Site"
MIMout <- suppressWarnings(
  as.data.frame(data) %>% full_join(as.data.frame(table))
)

MIMout$ANPP <- ANPP

ggplot(MIMout, aes(x=ANPP, y=MIMSOC, color=CLAY)) + geom_point() + 
  ggtitle("MIMICS estimated SOC vs estimated ANPP")
    

#ANPP vs SOC
r2_test <- cor.test(MIMout$SOC, MIMout$pGPP)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

ggplot(MIMout, aes(x=ANPP, y=SOC, color=CLAY)) + geom_point() + 
  ggtitle("Field SOC stocks vs estimated ANPP") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 200, y = 11, size = 3, colour = "dark blue")

```




