---
title: "Port over soil water constraint (fW) to MIMICS sandbox"
output:
  html_document:
    code_folding: show
---

```{r echo=FALSE, message=FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(knitr)
library(DT)
library(gridExtra)
library(grid)
library(reshape2)
library(scales)
library(rootSolve)
library(boot)

options(width = 100)
```


#### Simple steps:

1. Calculate fW from soil water input.
2. Multiply Vmax by fW (fW value then regulates the max rate for microbial decomposition in the model).

In higher temporal resolution versions of MIMICS fW is more complex, i.e. fW is derived from water filled pore space and air filled pore space, thus connecting the water control over microbial dynamics to soil texture. I don't see anything in the MIMICS code that attempts to deal with microbial processing limitation in saturated soils. I'm guessing an assumption is being made that all soils are well drained. Thus, higher fW = greater max rate of microbial processing of SOM.

<br>

#### Question becomes, how to scale fW?
- The chosen range of possible fW values (e.g. 0-1, 0-0.5, etc.) equates to how much limitation on microbial processing is imparted by the soil water input values we're using.
- Residuals from previous modle runs are ~2x off 1:1 line, so let's start with a max water control of 50%


```{r}
# get RC pt data
predMAP_pts <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_predMAP_112320.csv", as.is=T)

# scale predicted MAP from 0.5 to 1 ==> fW
predMAP_pts$fW <- rescale(predMAP_pts$pred_MAP, to = c(0.5, 1), from = range(predMAP_pts$pred_MAP, na.rm = TRUE, finite = TRUE))

#remove rows with missing data and save dataframe to csv 
#write.csv(na.omit(predMAP_pts), "C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv")

print(na.omit(predMAP_pts[1:24,c(3:7,9:11,29,30)]), row.names = FALSE)

```
62 points total

***

#### Applying fW to the MIMICS sandbox code
Nothing complicated. Add fW as multiplier in final calculation of fW

> VMAX = Vmax * v_MOD * fW  

#### Run MIMICS and see what happens...

```{r , message=FALSE, results=FALSE}
# -----------------------------------------------------------
# MIMICS2_testing_reverseSTODEonly
# -----------------------------------------------------------

#REVERSE MODEL 
RXEQ <- function(t, y, pars) {
  with (as.list(c(y, pars)),{
    
    #Flows to and from MIC_1
    LITmin[1] = MIC_1 * VMAX[1] * LIT_1 / (KM[1] + MIC_1)   #MIC_1 decomp of MET lit
    LITmin[2] = MIC_1 * VMAX[2] * LIT_2 / (KM[2] + MIC_1)   #MIC_1 decomp of STRUC lit
    MICtrn[1] = MIC_1 * tau[1]  * fPHYS[1]                  #MIC_1 turnover to PHYSICAL SOM 
    MICtrn[2] = MIC_1 * tau[1]  * fCHEM[1]                  #MIC_1 turnover to CHEMICAL SOM  
    MICtrn[3] = MIC_1 * tau[1]  * fAVAI[1]                  #MIC_1 turnover to AVAILABLE SOM  
    SOMmin[1] = MIC_1 * VMAX[3] * SOM_3 / (KM[3] + MIC_1)   #decomp of SOMa by MIC_1
    
    #Flows to and from MIC_2
    LITmin[3] = MIC_2 * VMAX[4] * LIT_1 / (KM[4] + MIC_2)   #decomp of MET litter
    LITmin[4] = MIC_2 * VMAX[5] * LIT_2 / (KM[5] + MIC_2)   #decomp of SRUCTURAL litter
    MICtrn[4] = MIC_2 * tau[2]  * fPHYS[2]                  #MIC_2 turnover to PHYSICAL  SOM 
    MICtrn[5] = MIC_2 * tau[2]  * fCHEM[2]                  #MIC_2 turnover to CHEMICAL  SOM  
    MICtrn[6] = MIC_2 * tau[2]  * fAVAI[2]                  #MIC_2 turnover to AVAILABLE SOM  
    SOMmin[2] = MIC_2 * VMAX[6] * SOM_3 / (KM[6] + MIC_2)   #decomp of SOMa by MIC_2
    
    DEsorb    = SOM_1 * desorb  #* (MIC_1 + MIC_2)  	#desorbtion of PHYS to AVAIL (function of fCLAY)
    OXIDAT    = ((MIC_1 * VMAX[2] * SOM_2 / (KO[1]*KM[2] + MIC_1)) +
                 (MIC_2 * VMAX[5] * SOM_2 / (KO[2]*KM[5] + MIC_2)) )  #oxidation of C to A

    dLIT_1 = I[1]*(1-FI[1]) - LITmin[1] - LITmin[3]
    dMIC_1 = CUE[1]*(LITmin[1]+ SOMmin[1]) + CUE[2]*(LITmin[2]) - sum(MICtrn[1:3])
    dSOM_1 = I[1]*FI[1] + MICtrn[1] + MICtrn[4]- DEsorb 
    
    dLIT_2 = I[2] * (1-FI[2]) - LITmin[2] - LITmin[4]
    dMIC_2 = CUE[3]*(LITmin[3]+ SOMmin[2]) + CUE[4]*(LITmin[4]) - sum(MICtrn[4:6])  
    dSOM_2 = I[2]*FI[2] + MICtrn[2] + MICtrn[5] - OXIDAT
    
    dSOM_3 = MICtrn[3] + MICtrn[6] + DEsorb + OXIDAT - SOMmin[1] - SOMmin[2]
    
    list(c(dLIT_1, dLIT_2, dMIC_1, dMIC_2, dSOM_1, dSOM_2, dSOM_3))
  })
}

#---------------------------------------------------------
# ---- Main program -------
#---------------------------------------------------------

#---------------------------------------------------------
# (A)       Read in parameters and site level data
#---------------------------------------------------------
  parameters <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv")
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  clay  <- data$CLAY2/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- ANPP[i] / (365*24)         # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV
    Km       <- exp(TSOI * Kslope + Kint) * aK
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                  #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD * (FW)      #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
MIM_fW_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=ASPECT_CLA)) + geom_point() +
  xlim(0,10) +
  ylim(0,10) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  ggtitle("MIMICS w/ fW")

```
```{r, echo=FALSE, message=FALSE, results=FALSE}
# -----------------------------------------------------------
# MIMICS2_testing_reverseSTODEonly
# -----------------------------------------------------------


### RUN MIMICS WITHOUT fW for comparison

#REVERSE MODEL 
RXEQ <- function(t, y, pars) {
  with (as.list(c(y, pars)),{
    
    #Flows to and from MIC_1
    LITmin[1] = MIC_1 * VMAX[1] * LIT_1 / (KM[1] + MIC_1)   #MIC_1 decomp of MET lit
    LITmin[2] = MIC_1 * VMAX[2] * LIT_2 / (KM[2] + MIC_1)   #MIC_1 decomp of STRUC lit
    MICtrn[1] = MIC_1 * tau[1]  * fPHYS[1]                  #MIC_1 turnover to PHYSICAL SOM 
    MICtrn[2] = MIC_1 * tau[1]  * fCHEM[1]                  #MIC_1 turnover to CHEMICAL SOM  
    MICtrn[3] = MIC_1 * tau[1]  * fAVAI[1]                  #MIC_1 turnover to AVAILABLE SOM  
    SOMmin[1] = MIC_1 * VMAX[3] * SOM_3 / (KM[3] + MIC_1)   #decomp of SOMa by MIC_1
    
    #Flows to and from MIC_2
    LITmin[3] = MIC_2 * VMAX[4] * LIT_1 / (KM[4] + MIC_2)   #decomp of MET litter
    LITmin[4] = MIC_2 * VMAX[5] * LIT_2 / (KM[5] + MIC_2)   #decomp of SRUCTURAL litter
    MICtrn[4] = MIC_2 * tau[2]  * fPHYS[2]                  #MIC_2 turnover to PHYSICAL  SOM 
    MICtrn[5] = MIC_2 * tau[2]  * fCHEM[2]                  #MIC_2 turnover to CHEMICAL  SOM  
    MICtrn[6] = MIC_2 * tau[2]  * fAVAI[2]                  #MIC_2 turnover to AVAILABLE SOM  
    SOMmin[2] = MIC_2 * VMAX[6] * SOM_3 / (KM[6] + MIC_2)   #decomp of SOMa by MIC_2
    
    DEsorb    = SOM_1 * desorb  #* (MIC_1 + MIC_2)  	#desorbtion of PHYS to AVAIL (function of fCLAY)
    OXIDAT    = ((MIC_1 * VMAX[2] * SOM_2 / (KO[1]*KM[2] + MIC_1)) +
                 (MIC_2 * VMAX[5] * SOM_2 / (KO[2]*KM[5] + MIC_2)) )  #oxidation of C to A

    dLIT_1 = I[1]*(1-FI[1]) - LITmin[1] - LITmin[3]
    dMIC_1 = CUE[1]*(LITmin[1]+ SOMmin[1]) + CUE[2]*(LITmin[2]) - sum(MICtrn[1:3])
    dSOM_1 = I[1]*FI[1] + MICtrn[1] + MICtrn[4]- DEsorb 
    
    dLIT_2 = I[2] * (1-FI[2]) - LITmin[2] - LITmin[4]
    dMIC_2 = CUE[3]*(LITmin[3]+ SOMmin[2]) + CUE[4]*(LITmin[4]) - sum(MICtrn[4:6])  
    dSOM_2 = I[2]*FI[2] + MICtrn[2] + MICtrn[5] - OXIDAT
    
    dSOM_3 = MICtrn[3] + MICtrn[6] + DEsorb + OXIDAT - SOMmin[1] - SOMmin[2]
    
    list(c(dLIT_1, dLIT_2, dMIC_1, dMIC_2, dSOM_1, dSOM_2, dSOM_3))
  })
}

#---------------------------------------------------------
# ---- Main program -------
#---------------------------------------------------------

#---------------------------------------------------------
# (A)       Read in parameters and site level data
#---------------------------------------------------------
  parameters <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv")
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  clay  <- data$CLAY2/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- ANPP[i] / (365*24)         # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV
    Km       <- exp(TSOI * Kslope + Kint) * aK
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                  #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD       #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
MIM_no_fW_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=ASPECT_CLA)) + geom_point() +
  xlim(0,10) +
  ylim(0,10) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  ggtitle("MIMICS w/o fW")

```

<br>

```{r warning=FALSE, echo=FALSE, results=FALSE}
grid.arrange(MIM_fW_plot, MIM_no_fW_plot)


```

<br>

##### Maybe we're now lowering fW too much, let's give it a boost to make up for the down regulation from fW


