---
title: "RCrk MIMICS: fMET Control"
output:
  html_document:
    code_folding: hide
---

```{r echo=FALSE, message=FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(knitr)
library(DT)
library(gridExtra)
library(grid)
library(reshape2)
library(scales)
library(rootSolve)
library(boot)
library(viridis)

options(width = 100)

dir <- '/GitHub/MIMICS-RCrk/MIMICS-DP/' 
setwd(dir)
```

```{r echo=FALSE, message=FALSE}
# -----------------------------------------------------------
# MIMICS2_RXEQ function
# -----------------------------------------------------------

#REVERSE MODEL 
RXEQ <- function(t, y, pars) {
  with (as.list(c(y, pars)),{
    
    #Flows to and from MIC_1
    LITmin[1] = MIC_1 * VMAX[1] * LIT_1 / (KM[1] + MIC_1)   #MIC_1 decomp of MET lit
    LITmin[2] = MIC_1 * VMAX[2] * LIT_2 / (KM[2] + MIC_1)   #MIC_1 decomp of STRUC lit
    MICtrn[1] = MIC_1 * tau[1]  * fPHYS[1]                  #MIC_1 turnover to PHYSICAL SOM 
    MICtrn[2] = MIC_1 * tau[1]  * fCHEM[1]                  #MIC_1 turnover to CHEMICAL SOM  
    MICtrn[3] = MIC_1 * tau[1]  * fAVAI[1]                  #MIC_1 turnover to AVAILABLE SOM  
    SOMmin[1] = MIC_1 * VMAX[3] * SOM_3 / (KM[3] + MIC_1)   #decomp of SOMa by MIC_1
    
    #Flows to and from MIC_2
    LITmin[3] = MIC_2 * VMAX[4] * LIT_1 / (KM[4] + MIC_2)   #decomp of MET litter
    LITmin[4] = MIC_2 * VMAX[5] * LIT_2 / (KM[5] + MIC_2)   #decomp of SRUCTURAL litter
    MICtrn[4] = MIC_2 * tau[2]  * fPHYS[2]                  #MIC_2 turnover to PHYSICAL  SOM 
    MICtrn[5] = MIC_2 * tau[2]  * fCHEM[2]                  #MIC_2 turnover to CHEMICAL  SOM  
    MICtrn[6] = MIC_2 * tau[2]  * fAVAI[2]                  #MIC_2 turnover to AVAILABLE SOM  
    SOMmin[2] = MIC_2 * VMAX[6] * SOM_3 / (KM[6] + MIC_2)   #decomp of SOMa by MIC_2
    
    DEsorb    = SOM_1 * desorb  #* (MIC_1 + MIC_2)  	#desorbtion of PHYS to AVAIL (function of fCLAY)
    OXIDAT    = ((MIC_1 * VMAX[2] * SOM_2 / (KO[1]*KM[2] + MIC_1)) +
                 (MIC_2 * VMAX[5] * SOM_2 / (KO[2]*KM[5] + MIC_2)) )  #oxidation of C to A

    dLIT_1 = I[1]*(1-FI[1]) - LITmin[1] - LITmin[3]
    dMIC_1 = CUE[1]*(LITmin[1]+ SOMmin[1]) + CUE[2]*(LITmin[2]) - sum(MICtrn[1:3])
    dSOM_1 = I[1]*FI[1] + MICtrn[1] + MICtrn[4]- DEsorb 
    
    dLIT_2 = I[2] * (1-FI[2]) - LITmin[2] - LITmin[4]
    dMIC_2 = CUE[3]*(LITmin[3]+ SOMmin[2]) + CUE[4]*(LITmin[4]) - sum(MICtrn[4:6])  
    dSOM_2 = I[2]*FI[2] + MICtrn[2] + MICtrn[5] - OXIDAT
    
    dSOM_3 = MICtrn[3] + MICtrn[6] + DEsorb + OXIDAT - SOMmin[1] - SOMmin[2]
    
    list(c(dLIT_1, dLIT_2, dMIC_1, dMIC_2, dSOM_1, dSOM_2, dSOM_3))
  })
}
```

***

### fMET

What is the influence of the fMET parameter in the MIMICS model? 

Thus far, I've been using the mean LiDET litter fMET value. Plots below observe effects on the model mirobial and SOC pools when using the mean (0.384), minimum (0.148) and maximum (0.76) fMET parameter values in the LiDET dataset.

***

```{r message=FALSE, results=FALSE, warning=FALSE, out.width = '50%'}
#---------------------------------------------------------
# ---- MIMICS: Mean LiDET fMET -------
#---------------------------------------------------------

  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+400)/2
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV  #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=pGPP)) + geom_point() +
  scale_color_gradient(low="blue", high="red") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("fMET = 0.384 (LiDET mean)") + 
  xlim(0,15)
MIM_plot

#save data table for use later
colnames(table)[1] <- "Site"
mean_fmet <- suppressWarnings(
  as.data.frame(data) %>% full_join(as.data.frame(table))
)
```
```{r message=FALSE, results=FALSE, warning=FALSE, out.width = '50%'}
#---------------------------------------------------------
# ---- MIMICS: Min LiDET fMET -------
#---------------------------------------------------------

  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+400)/2
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- min(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV  #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=pGPP)) + geom_point() +
  scale_color_gradient(low="blue", high="red") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("fMET = 0.148 (LiDET min)") + 
  xlim(0,15)
MIM_plot

#save data table for use later
colnames(table)[1] <- "Site"
min_fmet <- suppressWarnings(
  as.data.frame(data) %>% full_join(as.data.frame(table))
)
```
```{r message=FALSE, results=FALSE, warning=FALSE, out.width = '50%'}
#---------------------------------------------------------
# ---- MIMICS: Max LiDET fMET -------
#---------------------------------------------------------

  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+400)/2
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- max(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV  #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=pGPP)) + geom_point() +
  scale_color_gradient(low="blue", high="red") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("fMET = 0.76 (LiDET max)") + 
  xlim(0,15)
MIM_plot

#save data table for use later
colnames(table)[1] <- "Site"
max_fmet <- suppressWarnings(
  as.data.frame(data) %>% full_join(as.data.frame(table))
)

```

***

#### Why only a minor effect on SOC estimate when changing fMET value?

**- fMET controls the ratio of C passed to either the r or K microbial pools.** 

**- Next, let's visualize how fMET is changing these microbial pool sizes.**

***

```{r message=FALSE, results=FALSE, out.width = '70%', warning=FALSE}

#prep data
min_fmet$MICr2 <- round(as.numeric(levels(min_fmet$MICr))[min_fmet$MICr],3)
min_fmet$MICK2 <- round(as.numeric(levels(min_fmet$MICK))[min_fmet$MICK],3)

#melt data
min_fmet_melt <- min_fmet %>% gather(key = 'MIC_type', value = 'MIC_size', MICr2:MICK2)

ggplot(min_fmet_melt, aes(x=signif(pGPP+400, floor(log10(pGPP))), y=MIC_size, fill=MIC_type)) +
         theme_bw() +
         geom_bar(position="stack", stat = "summary", fun.y = "mean", width=20) +
         scale_fill_manual(values=c("#1f3c88", "#ee6f57"), labels=c("MIC-K","MIC-r")) + labs(fill="MIC Pool") +
  theme(axis.text.x=element_text(angle=90, hjust=0)) +
  xlab("Estimated GPP") + 
  ylab("Microbial Pool Size") +
  ggtitle("Min LiDET fMET")
        
```

```{r message=FALSE, results=FALSE, out.width = '70%', warning=FALSE}

#prep data
mean_fmet$MICr2 <- round(as.numeric(levels(mean_fmet$MICr))[mean_fmet$MICr],3)
mean_fmet$MICK2 <- round(as.numeric(levels(mean_fmet$MICK))[mean_fmet$MICK],3)

#melt data
mean_fmet_melt <- mean_fmet %>% gather(key = 'MIC_type', value = 'MIC_size', MICr2:MICK2)

ggplot(mean_fmet_melt, aes(x=signif(pGPP+400, floor(log10(pGPP))), y=MIC_size, fill=MIC_type)) +
         theme_bw() +
         geom_bar(position="stack", stat = "summary", fun.y = "mean", width=20) +
         scale_fill_manual(values=c("#1f3c88", "#ee6f57"), labels=c("MIC-K","MIC-r")) + labs(fill="MIC Pool") +
  theme(axis.text.x=element_text(angle=90, hjust=0)) +
  xlab("Estimated GPP") + 
  ylab("Microbial Pool Size") +
  ggtitle("Mean LiDET fMET")
        
```

```{r message=FALSE, results=FALSE, out.width = '70%', warning=FALSE}

#prep data
max_fmet$MICr2 <- round(as.numeric(levels(max_fmet$MICr))[max_fmet$MICr],3)
max_fmet$MICK2 <- round(as.numeric(levels(max_fmet$MICK))[max_fmet$MICK],3)

#melt data
max_fmet_melt <- max_fmet %>% gather(key = 'MIC_type', value = 'MIC_size', MICr2:MICK2)

ggplot(max_fmet_melt, aes(x=signif(pGPP+400, floor(log10(pGPP))), y=MIC_size, fill=MIC_type)) +
         theme_bw() +
         geom_bar(position="stack", stat = "summary", fun.y = "mean", width=20) +
         scale_fill_manual(values=c("#1f3c88", "#ee6f57"), labels=c("MIC-K","MIC-r")) + labs(fill="MIC Pool") +
  theme(axis.text.x=element_text(angle=90, hjust=0)) +
  xlab("Estimated GPP") + 
  ylab("Microbial Pool Size") +
  ggtitle("Max LiDET fMET")
        
```

***

#### A higher fMET sends more litter C to the r strategists. How does this effect SOM pools?

***

```{r message=FALSE, results=FALSE, out.width = '70%', warning=FALSE}

#prep data
min_fmet$SOMp2 <- round(as.numeric(levels(min_fmet$SOMp))[min_fmet$SOMp],3)
min_fmet$SOMc2 <- round(as.numeric(levels(min_fmet$SOMc))[min_fmet$SOMc],3)
min_fmet$SOMa2 <- round(as.numeric(levels(min_fmet$SOMa))[min_fmet$SOMa],3)

#melt data
min_fmet_melt <- min_fmet %>% gather(key = 'SOM_pool', value = 'SOM_size', SOMp2:SOMa2)

ggplot(min_fmet_melt, aes(x=signif(pGPP+400, floor(log10(pGPP))), y=SOM_size, fill=SOM_pool)) +
         theme_bw() +
         geom_bar(position="stack", stat = "summary", fun.y = "mean", width=20) +
         scale_fill_manual(values=c("#59886b", "#ffc85c", "#c05555"), labels=c("SOMa","SOMc", "SOMp")) + labs(fill="SOM Pool") +
  theme(axis.text.x=element_text(angle=90, hjust=0)) +
  xlab("Estimated GPP") + 
  ylab("SOM Pool Size") +
  ggtitle("Min LiDET fMET")
        
```

```{r message=FALSE, results=FALSE, out.width = '70%', warning=FALSE}

#prep data
mean_fmet$SOMp2 <- round(as.numeric(levels(mean_fmet$SOMp))[mean_fmet$SOMp],3)
mean_fmet$SOMc2 <- round(as.numeric(levels(mean_fmet$SOMc))[mean_fmet$SOMc],3)
mean_fmet$SOMa2 <- round(as.numeric(levels(mean_fmet$SOMa))[mean_fmet$SOMa],3)

#melt data
mean_fmet_melt <- mean_fmet %>% gather(key = 'SOM_pool', value = 'SOM_size', SOMp2:SOMa2)

ggplot(mean_fmet_melt, aes(x=signif(pGPP+400, floor(log10(pGPP))), y=SOM_size, fill=SOM_pool)) +
         theme_bw() +
         geom_bar(position="stack", stat = "summary", fun.y = "mean", width=20) +
         scale_fill_manual(values=c("#59886b", "#ffc85c", "#c05555"), labels=c("SOMa","SOMc", "SOMp")) + labs(fill="SOM Pool") +
  theme(axis.text.x=element_text(angle=90, hjust=0)) +
  xlab("Estimated GPP") + 
  ylab("SOM Pool Size") +
  ggtitle("Mean LiDET fMET")
        
```

```{r message=FALSE, results=FALSE, out.width = '70%', warning=FALSE}

#prep data
max_fmet$SOMp2 <- round(as.numeric(levels(max_fmet$SOMp))[max_fmet$SOMp],3)
max_fmet$SOMc2 <- round(as.numeric(levels(max_fmet$SOMc))[max_fmet$SOMc],3)
max_fmet$SOMa2 <- round(as.numeric(levels(max_fmet$SOMa))[max_fmet$SOMa],3)

#melt data
max_fmet_melt <- max_fmet %>% gather(key = 'SOM_pool', value = 'SOM_size', SOMp2:SOMa2)

ggplot(max_fmet_melt, aes(x=signif(pGPP+400, floor(log10(pGPP))), y=SOM_size, fill=SOM_pool)) +
         theme_bw() +
         geom_bar(position="stack", stat = "summary", fun.y = "mean", width=20) +
         scale_fill_manual(values=c("#59886b", "#ffc85c", "#c05555"), labels=c("SOMa","SOMc", "SOMp")) + labs(fill="SOM Pool") +
  theme(axis.text.x=element_text(angle=90, hjust=0)) +
  xlab("Estimated GPP") + 
  ylab("SOM Pool Size") +
  ggtitle("Max LiDET fMET")
        
```

***

### fMET Conclusion

***

#### Overall , the effect on SOM from a higher fMET value is a greater amount of physically protected SOM, coming at the expense of chemically protected SOM. The available SOM pool is largely unaffected by the fMET value. 

**- fMET good to tweak for matching pool ratios in Hasini data.**

**- fMET not a parameter that influences total SOC estimates.**


</br>
