---
title: "RCrk MIMICS sandbox in progress"
output:
  html_document:
    code_folding: hide
---

```{r echo=FALSE, message=FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(knitr)
library(DT)
library(gridExtra)
library(grid)
library(reshape2)
library(scales)
library(rootSolve)
library(boot)

options(width = 100)
```

***

### 1. First MIMICS run: Straight out of the box...

- No changes from raw sandbox MIMICS script based on LiDeT
- A perfect model fit would place all points on the dashed 1:1 line

```{r echo=FALSE, message=FALSE}
# -----------------------------------------------------------
# MIMICS2_testing_reverseSTODEonly
# -----------------------------------------------------------
# Will Wieder
# Oct 23, 2013
# Modified Aug, 2015; April 2016; Sept 2020
# Solve a system of non-linear equations for enzyme SOC solution
# uses packages deSolve / rootSolve

# Single layer model with: 
# 2 litter C pools (LIT), corresponding to metabolic and structural litter.
# 2 microbial pool (MIC; i.e. r vs. K strategists)
# 3 SOM pools corresponding to physically & chemically protected & available pools

# -----------------------------------------------------------
# (A) Reads in site level data from LTER sites
# (B) Calculates steady state C pools using RXEQ & STODE function
# -----------------------------------------------------------


#dir <- '/Users/wwieder/Will/git_repos_local/MIMICS/'
dir <- '/GitHub/MIMICS-RCrk/MIMICS-DP/' 
setwd(dir)

#REVERSE MODEL 
RXEQ <- function(t, y, pars) {
  with (as.list(c(y, pars)),{
    
    #Flows to and from MIC_1
    LITmin[1] = MIC_1 * VMAX[1] * LIT_1 / (KM[1] + MIC_1)   #MIC_1 decomp of MET lit
    LITmin[2] = MIC_1 * VMAX[2] * LIT_2 / (KM[2] + MIC_1)   #MIC_1 decomp of STRUC lit
    MICtrn[1] = MIC_1 * tau[1]  * fPHYS[1]                  #MIC_1 turnover to PHYSICAL SOM 
    MICtrn[2] = MIC_1 * tau[1]  * fCHEM[1]                  #MIC_1 turnover to CHEMICAL SOM  
    MICtrn[3] = MIC_1 * tau[1]  * fAVAI[1]                  #MIC_1 turnover to AVAILABLE SOM  
    SOMmin[1] = MIC_1 * VMAX[3] * SOM_3 / (KM[3] + MIC_1)   #decomp of SOMa by MIC_1
    
    #Flows to and from MIC_2
    LITmin[3] = MIC_2 * VMAX[4] * LIT_1 / (KM[4] + MIC_2)   #decomp of MET litter
    LITmin[4] = MIC_2 * VMAX[5] * LIT_2 / (KM[5] + MIC_2)   #decomp of SRUCTURAL litter
    MICtrn[4] = MIC_2 * tau[2]  * fPHYS[2]                  #MIC_2 turnover to PHYSICAL  SOM 
    MICtrn[5] = MIC_2 * tau[2]  * fCHEM[2]                  #MIC_2 turnover to CHEMICAL  SOM  
    MICtrn[6] = MIC_2 * tau[2]  * fAVAI[2]                  #MIC_2 turnover to AVAILABLE SOM  
    SOMmin[2] = MIC_2 * VMAX[6] * SOM_3 / (KM[6] + MIC_2)   #decomp of SOMa by MIC_2
    
    DEsorb    = SOM_1 * desorb  #* (MIC_1 + MIC_2)  	#desorbtion of PHYS to AVAIL (function of fCLAY)
    OXIDAT    = ((MIC_1 * VMAX[2] * SOM_2 / (KO[1]*KM[2] + MIC_1)) +
                 (MIC_2 * VMAX[5] * SOM_2 / (KO[2]*KM[5] + MIC_2)) )  #oxidation of C to A

    dLIT_1 = I[1]*(1-FI[1]) - LITmin[1] - LITmin[3]
    dMIC_1 = CUE[1]*(LITmin[1]+ SOMmin[1]) + CUE[2]*(LITmin[2]) - sum(MICtrn[1:3])
    dSOM_1 = I[1]*FI[1] + MICtrn[1] + MICtrn[4]- DEsorb 
    
    dLIT_2 = I[2] * (1-FI[2]) - LITmin[2] - LITmin[4]
    dMIC_2 = CUE[3]*(LITmin[3]+ SOMmin[2]) + CUE[4]*(LITmin[4]) - sum(MICtrn[4:6])  
    dSOM_2 = I[2]*FI[2] + MICtrn[2] + MICtrn[5] - OXIDAT
    
    dSOM_3 = MICtrn[3] + MICtrn[6] + DEsorb + OXIDAT - SOMmin[1] - SOMmin[2]
    
    list(c(dLIT_1, dLIT_2, dMIC_1, dMIC_2, dSOM_1, dSOM_2, dSOM_3))
  })
}
```


```{r message=FALSE, results=FALSE}

#---------------------------------------------------------
# ---- Main program -------
#---------------------------------------------------------

#---------------------------------------------------------
# (A)       Read in parameters and site level data
#---------------------------------------------------------
  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  #ANPP  <- data$pGPP+400
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV  #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=L1)) + geom_point() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Color: Watershed")
MIM_plot

MIM_plot2 <- ggplot(data, aes(x=MIMSOC, y=SOC, color=ASPECT_CLA)) + geom_point() +
  #scale_color_gradient2(midpoint=midp, low="blue", mid="green", high="red", space ="Lab" ) +
  #xlim(0,10) +
  #ylim(0,10) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Color: Aspect class")
MIM_plot2
```

##### Simply shows what we're starting with. Predicted SOC is mostly too high and there's a large spike across the Johnston Draw soil samples. 

- By far the greatest number of samples in the input dataset are from Johnston Draw, so what's happening there is likely present across other regions of RCrk, we just can see it.

- Aspect appears to be driving at least part of the discrepancy in Johnston. Other mapping work also shows that the ANPP values we're using here are coarse (innacurate relative to the specific soil sample locations)

<br>

***

### 2. Updated ANPP to use GPP from MSAVI relationship raster

- MSAVI equation relating MSAVI to GPP result in a large number of negative values across RCrk. This throws a wrench in MIMICS, so the GPP values are all +400 to eliminate the negative values.

- GPP values are divided by two to approximate ANPP

```{r message=FALSE, results=FALSE}
#---------------------------------------------------------
# ---- Main program -------
#---------------------------------------------------------

#---------------------------------------------------------
# (A)       Read in parameters and site level data
#---------------------------------------------------------
  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+400)/2
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint) * aV  #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=L1)) + geom_point() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Color: Watershed")
MIM_plot

MIM_plot2 <- ggplot(data, aes(x=MIMSOC, y=SOC, color=ASPECT_CLA)) + geom_point() +
  #scale_color_gradient2(midpoint=midp, low="blue", mid="green", high="red", space ="Lab" ) +
  #xlim(0,10) +
  #ylim(0,10) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Color: Aspect class")
MIM_plot2
```

<br>

***

### 3. Tweak model parameters
Mostly exploratory trial and error at this stage, not fine tuned, but effective at improving residuals.

- Vint * 2
- Kint / 2


```{r message=FALSE, results=FALSE}
#---------------------------------------------------------
# ---- Main program -------
#---------------------------------------------------------

#---------------------------------------------------------
# (A)       Read in parameters and site level data
#---------------------------------------------------------
  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+400)/2
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint*2) * aV   #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint/2) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD #* FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$MIMLIT <- MIMLIT
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=L1)) + geom_point() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Color: Watershed")
MIM_plot

MIM_plot2 <- ggplot(data, aes(x=MIMSOC, y=SOC, color=ASPECT_CLA)) + geom_point() +
  #scale_color_gradient2(midpoint=midp, low="blue", mid="green", high="red", space ="Lab" ) +
  #xlim(0,10) +
  #ylim(0,10) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Color: Aspect class")
MIM_plot2

MIM_plot3 <- ggplot(data, aes(x=MIMMIC, y=SOC, color=pGPP+400)) + geom_point() +
  #scale_color_gradient2(midpoint=midp, low="blue", mid="green", high="red", space ="Lab" ) +
  #xlim(0,10) +
  #ylim(0,10) +
  #geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  #annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Microbial pool (MIMMIC)")
MIM_plot3

MIM_plot4 <- ggplot(data, aes(x=MIMLIT, y=SOC, color=pGPP+400)) + geom_point() +
  #scale_color_gradient2(midpoint=midp, low="blue", mid="green", high="red", space ="Lab" ) +
  #xlim(0,10) +
  #ylim(0,10) +
  #geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  #annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Litter pool (MIMLIT)")
MIM_plot4
```


<br>

##### Litter pools too low...?
- Microbial pool on the low side, but perhaps okay?
- More tweaking to do!

<br>


***

### 4. Add scaler for soil moisture to impart control on microbial activity
- Converts mean annual precip to value between 0-1 (fW)
- Multiply Vmax (microbial max decomp rate) by fW to limit microbial activity in low moisture conditions. No mechanisms implemented to limit microbes under saturated conditions (rare at RCrk?), so fW is a simple limiter.

```{r message=FALSE, results=FALSE}
#---------------------------------------------------------
# ---- Main program -------
#---------------------------------------------------------

#---------------------------------------------------------
# (A)       Read in parameters and site level data
#---------------------------------------------------------
  para_file <- paste("C:/GitHub/MIMICS-RCrk/MIMICS-DP/MIMICS_parameters/parameters_LIDET-MIM-REV.csv", sep = "") 
  parameters <- read.csv(para_file)
  names(parameters)
  attach(parameters)
  depth <- parameters$depth[1]
  
  litter <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Litter_Characteristics/LIDET_LitterCharacteristics.csv")
  litter <- litter[1:6,]   #subset foliar litter only 
  attach(litter)
  calcN    <- (1 / litCN) / 2.5 * 100    
  lit_fMET <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * litLIG / calcN)   
  
  data <- read.csv("C:/GitHub/MIMICS-RCrk/MIMICS-DP/Site_data/MIMICS_pts_pMAP_fW_112320.csv") #site level forcing variables
  names(data)
  attach(data)
  
  KO <- parameters$KO
  #ANPP  <- data$ANPP / 2           		# if needed convert to gC/m2/y from g/m2/y
  ANPP  <- (data$pGPP+400)/2
  clay  <- data$CLAY/100  				    # if needed, convert from % clay to fraction
  tsoi  <- MAT
  nsites<- length(Site)
  
  lig    <- LIG #/ 100
  Nnew   <- N                                                  #N in litter additions
  fMET1  <- fmet_p[1] * (fmet_p[2] - fmet_p[3] * lig / Nnew)   #as partitioned in Daycent
  MIMLIT <- rep(NA, nsites)           	                       #Vector for results
  MIMMIC <- rep(NA, nsites)           
  MIM_CO <- rep(NA, nsites)           
  MIMSOC <- rep(NA, nsites)           
  
  strSite <- as.character(data$Site)                           #convert site names to string
  pools  <- c('site','LITm', 'LITs', 'MICr', 'MICK', 'SOMp', 'SOMc', 'SOMa')
  table  <- array(NA, dim=c(nsites,8), dimnames=list(as.character(Site),pools)) 
  table[,1]       <- as.character(Site)
  
  POOLS  <- c("LIT","MIC","SOC")
  npools <- length(POOLS)  
  LITpool<- c('LITm', 'LITs') 
  MICpool<- c('MICr', 'MICk') 
  SOMpool<- c('SOMp', 'SOMa','SOMc') 
  
  MIMLIT <- array(NA, dim=c(nsites))           	             # array for results
  MIMMIC <- array(NA, dim=c(nsites))           
  MIM_CO <- array(NA, dim=c(nsites))           
  MIMSOC <- array(NA, dim=c(nsites))           
  
  strSite <- as.character(data$Site)  #convert site names to string
  
  #Make vectors to store model results that match obs temporal resolution
  npts   <- 6*10*14   				#6 litter * 10 years * 14 sites
  xyLIT  <- rep(NA, npts) 
  xyTIME <- rep(NA, npts) 
  xySITE <- rep(NA, npts) 
  xyOBS  <- rep(NA, npts)
  xyMIM  <- rep(NA, npts)
  xyCount<- 1
  
  #-----------------------------------------------------------
  # (B)       RXEQ for site using STODE function
  # Starts Big loop over all sites (i) & all litter types (j)
  #-----------------------------------------------------------
  
  for (i in 1:nsites) {         #speeds up debugging     	
    # Read in site characteristics -----------
    print(paste("-------- starting ", data$Site[i], " --------") )
    
    fMET       <- mean(lit_fMET)           # uses mean litter fmet from LIDET
    # fMET       <- fMET1[i]                 # uses site estimate for fmet
    fCLAY      <- clay[i]
    TSOI       <- tsoi[i]
    FW         <- fW[i]                #<-- DPierson added fW
    EST_LIT_in <- (ANPP[i] / (365*24))        # gC/m2/h (from gC/m2/y)
    h2y        <- 24*365
    MICROtoECO <- depth * 1e4 * 1e-3         # mgC/cm3 to g/m2
    EST_LIT    <- EST_LIT_in  * 1e3 / 1e4    # mgC/cm2/h(from gC/m2/h) 
    
    # ------------ caclulate parameters ---------------
    Vmax     <- exp(TSOI * Vslope + Vint*2) * aV   #dp: Vint*2
    Km       <- exp(TSOI * Kslope + Kint/2) * aK  #dp: Kint/2
    
    #ANPP strongly correlated with MAP
    Tau_MOD1 <- sqrt(ANPP[i]/Tau_MOD[1])          # basicaily standardize against NWT
    Tau_MOD2 <- Tau_MOD[4]                        # increased 3-fold for SS SOC pools
    Tau_MOD1[Tau_MOD1 < Tau_MOD[2]] <- Tau_MOD[2] # correction not used in LIDET resutls 
    Tau_MOD1[Tau_MOD1 > Tau_MOD[3]] <- Tau_MOD[3] 
    tau <- c(tau_r[1]*exp(tau_r[2]*fMET), 
             tau_K[1]*exp(tau_K[2]*fMET))   
    tau <- tau * Tau_MOD1 * Tau_MOD2
    
    fPHYS    <- c(fPHYS_r[1] * exp(fPHYS_r[2]*fCLAY), 
                  fPHYS_K[1] * exp(fPHYS_K[2]*fCLAY)) 	            #fraction to SOMp
    fCHEM    <- c(fCHEM_r[1] * exp(fCHEM_r[2]*fMET) * fCHEM_r[3], 
                  fCHEM_K[1] * exp(fCHEM_K[2]*fMET) * fCHEM_K[3]) 	#fraction to SOMc
    fAVAI    <- 1- (fPHYS + fCHEM)
    desorb   <- fSOM_p[1] * exp(fSOM_p[2]*(fCLAY))                 #CHANGED FOR GLOBAL RUN!!!     
    
    #desorb   <- desorb/10 # modified as in MIMdef from Zhang et al 2020
    #fPHYS    <- fPHYS/5  # to reduce allocation to physically protected pool 5x
    
    pSCALAR  <- PHYS_scalar[1] * exp(PHYS_scalar[2]*(sqrt(fCLAY)))  #Scalar for texture effects on SOMp
    v_MOD    <- vMOD  # to avoid writing over orig. parameters
    k_MOD    <- kMOD 
    k_MOD[3] <- k_MOD[3] * pSCALAR    
    k_MOD[6] <- k_MOD[6] * pSCALAR    
    
    VMAX     <- Vmax * v_MOD * FW    #<-- DPierson added fW
    KM       <- Km / k_MOD
    
    #initialize pools
    I       <- array(NA, dim=2)              #Litter inputs to MET/STR
    I[1]    <- (EST_LIT / depth) * fMET     
    I[2]    <- (EST_LIT / depth) * (1-fMET)
    lit     <- I   
    mic     <- I  
    som     <- rep(NA, 3) 
    som[1]  <- I[1]
    som[2]  <- I[2]
    som[3]  <- I[1] 
    LITmin  <- rep(NA, dim=4)
    MICtrn  <- rep(NA, dim=6)
    SOMmin  <- rep(NA, dim=2)
    DEsorb  <- rep(NA, dim=1)
    OXIDAT  <- rep(NA, dim=1)
    
    #Calculate RXEQ pools  
    Tpars <- c( I = I, VMAX = VMAX, KM = KM, CUE = CUE, 
                fPHYS = fPHYS, fCHEM = fCHEM, fAVAI = fAVAI, FI = FI, 
                tau = tau, LITmin = LITmin, SOMmin = SOMmin, MICtrn = MICtrn, 
                desorb = desorb, DEsorb = DEsorb, OXIDAT = OXIDAT, KO = KO)
    Ty    <- c( LIT_1 = lit[1], LIT_2 = lit[2], 
                MIC_1 = mic[1], MIC_2 = mic[2], 
                SOM_1 = som[1], SOM_2 = som[2], SOM_3 = som[3] )
    test  <- stode(y = Ty, time = 1e6, fun = RXEQ, parms = Tpars, positive = TRUE)
    if (i == 2) {print(test[1])}
    remove(lit, mic, som)
  
    table[i,2:8] <- as.numeric(test[[1]])
    MIMLIT[i]    <- (test[[1]][[1]]+test[[1]][[2]])  * depth *1e4 / 1e6#convert kgC/m2 from mgC/cm3 (0-30 cm) 
    MIMMIC[i]    <- (test[[1]][[3]]+test[[1]][[4]])  * depth *1e4 / 1e6
    MIM_CO[i]    <-  test[[1]][[3]]/test[[1]][[4]]
    MIMSOC[i]    <- sum(test[[1]])  * depth *1e4 / 1e6   
    
    remove(test, Ty, Tpars, LITmin, MICtrn, SOMmin)
  
  } # close i loop (sites)
  
  
#plot results  
data$MIMSOC <- MIMSOC  
data$MIMMIC <- MIMMIC
data$MIMLIT <- MIMLIT
data$residual <- data$SOC-data$MIMSOC

# test correlation and model fit
r2_test <- cor.test(data$SOC, data$MIMSOC)
r_val <- round(as.numeric(unlist(r2_test ['estimate'])),3)

MIM_plot <- ggplot(data, aes(x=MIMSOC, y=SOC, color=L1)) + geom_point() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Color: Watershed")
MIM_plot

MIM_plot2 <- ggplot(data, aes(x=MIMSOC, y=SOC, color=ASPECT_CLA)) + geom_point() +
  #scale_color_gradient2(midpoint=midp, low="blue", mid="green", high="red", space ="Lab" ) +
  #xlim(0,10) +
  #ylim(0,10) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  annotate("text", label = paste0("r^2 = ", r_val), x = 4, y = 11, size = 3, colour = "dark blue") +
  ggtitle("Color: Aspect class")
MIM_plot2
```

##### fW has limited impact on residuals
- Perhaps Vmax is not the lever to sit on with fW?